### 2015-02-10 src/3_TimeSeries.tex
Adding Unit root tests

\subsection{Unit root tests}

@@

\newpage

@@

\section{Johansen method}

>>>>

@@

Many economic and financial time series exhibit trending behaviour or non-stationary behaviour in the mean or variance. An important econometric task is to determine the type of non-stationary. For trend stationary I(0) time series a time-trend regression is appropriate. For I(1) time series taking first differences transforms it into a stationary one.  For cointegration to determine if time series are I(1) is mandatory to model their long-run relationship. In order to determine if a time series is an a I(1) or I(0) process unit root tests are used. Several tests have been developed but the most widely used is an extension of the Dickey and Fuller test \cite{dickey1979} called the Augmented Dickey-Fuller (ADF) test developed in 1984 by Said and Dickey in 1984\cite{said1984}.

The ADF test tests the null hypothesis that a time series $y_t$ is I(1) against the alternative that it is I(0), assuming that the dynamics in the data have an ARMA structure. The ADF test is based on estimating the test regression:

\[
y_t = \boldsymbol{\beta}^\top
\]

@@
